Resolving Limits Faced by Classical Machine Learning Approaches:\\Areas of Application for Collaborative Interactive Learning Techniques

### 2018-06-29 paper.tex
Add clustering application section

\section{Algorithmic Foundations}
Bevor wir uns genauer den Anwendungen und Herausforderungen von CIL widmen, schauen wir uns 
zuerst vorhandene machine learning Strategien und Algorithmen an. Wie oben bereits angedeutet, 
gibt es eine Vielzahl an Definitionen für den Begriff ML\@. Hauptsächlich hat jedoch Arthur Samuel 
diesen Begriff im Jahr 1959 geprägt. Seitdem hat sich in diesem Bereich natürlich einiges geändert, 
jedoch gilt die Definition, dass ML Computern erlaubt Probleme zu lösen, ohne speziell dafür 
programmiert zu sein, heute immer noch\cite{MLStudiesUsingCheckers:samuel}.

Über die letzten Jahrzehnte hat sich ML stark weiterentwickelt und ist zu einem Bereich 
starken Forschungsinteresse vieler verschiedener Akteure geworden, was es schwierig macht, 
Lern-Strategien in verschiedene Kategorien einzuteilen. Unterschiedliche Forscher nutzen 
dazu verschiedene Ansätze\cite{FoundationsOfML:mohri}\cite{Structure:corne}. Im folgenden 
wollen wir fünf Strategien vorstellen\cite{FoundationsOfML:mohri}.

@@

\subsection{Unsupervised learning}
Im Gegensatz zu supervised learning erhält der Lernende mit dieser Technik ausschließlich 
unlabeled training data und macht Vorraussagen für alle ungesehene Punkte. Diese Technik ist 
relativ ähnlich zu der Art, wie Säuglinge neue Sachen lernen (Lernen von Sprache) und 
findet zum Beispiel Einsatz im Clustering von Daten in Gruppen\cite{BrainInf:holzinger}.

\subsection{Semi-supervised learning}
Wie der Name suggeriert erhält der Lernende bei dieser Technik Trainingsdaten, die sowohl aus 
labeled als auch aus unlabeled data besteht und macht Vorraussagen für alle ungesehenen Punkte.
Diese Technik wird hauptsählich in Bereichen eingesetzt, in denen Daten leicht zu erreichen sind, 
aber das finden von passenden Labels teuer ist.

\subsection{Reinforcement Learning}\label{reinforcement}
Reinforcement Learning ist der wohl älteste Ansatz und ein potentiell wichtiger Ansatz für CIL\@. 
Der Lernende interagiert mit seiner Umgebung, um neue Informationen zu gewinnen. Für jede Aktion 
erhält er eine Belohnung. Sein Ziel ist es über mehrere Wiederholungen seine Belohnung zu 
maximieren. Er befindet sich so jedoch im Zwiespalt zwischen der Entscheidung bereits gewonnene 
Information auszunutzen oder mehr Informationen durch weiter Aktionen zu erhalten.

\subsection{Active Learning}\label{active}
Das Ziel von Active Learning ist es, durch geschicktes interaktives Agieren mit anderen Agenten 
bereits vorhandene Datenpunkte zu beschriften und so eine ähnliche Performance bei weniger 
Informationen zu erreichen, wie in der Methode des supervised learning. Um das zu erreichen, 
benötigt der Lernende eine Auswahlstrategie\cite{ActiveToDedicated:calma}, die entscheidet ob 
eine Aktion einen ausreichend großen für das beschriften eines Datenpunkts bringt oder nicht.

\section{When is using CIL helpful?}\label{AdvantageOfCIL}
In etablierten ML Systemen muss für jede spezielle Anwendung ein eigenes Modell im Voraus 
entworfen und trainiert werden. ML Systeme haben also einen relativ schmalen Anwendungsrahmen. 
Die Idee bei CIL-Systemen ist, dass sie ein Leben lang lernen und selbstorganisiert Wissen 
aus verschiedenen Quellen sammeln und auswerten, um so gemeinsam mit anderen technischen 
und menschlichen Agenten kollaborierend und austauschend Probleme lösen\cite{CIL:sick}. 
Der CIL-Ansatz integriert also ganz bewusst andere intelligente Systeme 
(Menschen und Maschinen) in den Entscheidungsprozess, um für die einzelnen Entitäten 
ansonsten schwierige Probleme einfacher zu lösen.
Ein weiterer Unterschied zu klassischen Ansätzen stellt der wechselseitig Nutzen dar. 
Maschinen profitieren nicht nur von Trainingsdaten anderer Agenten, sondern leisten 
einen eigenen Beitrag, um Kollaborationsprozesse von Menschen aktiv zu unterstützen, indem 
sie ihre Wünsche und Bedürfnisse erkennen und entsprechend reagieren\cite{CIL:sick}.
\notes{D-CIL und O-CIL, obwohl man unterscheidet, betrachten wir hier nur allgemeines Modell.}

\section{Classification of CIL in Organic Computing}
CIL-Systeme können sozusagen teilweise als organisch strukturierte Informationstechnologie verstanden 
werden, die sogenannte Selbst-x-Eigenschaften erfüllen\cite{Organic:schloer}\cite{Organic:schmeck}, 
sich also 
\begin{itemize}
    \item selbst konfigurieren, in dem Sinn, dass sie nicht von Entwicklern auf einen 
        Anwendungsfall ausgerichtet werden, 
    \item selbst optimieren, indem sie verschiedene Strategien des ML anwenden, um ihr 
        Wissen zu erweitern, 
    \item und sich selbst heilen und schützen, da Kooperation mit anderen System möglich ist.
\end{itemize}
Je nachdem welche Methoden des ML eingesetzt werden, sind CIL-Systeme in der Entwicklung auch 
mehr oder weniger selbst erklärend\cite{Organic:schloer}.

\section{Application examples}
\subsection{Clustering}

@@

\begin{itemize}
    \item Clustering
        \begin{itemize}
            \item (clustering communities on Facebook for group target advertising (politics))
            \item Methods: k-Means, DJ-clustering? --> add paper ref
        \end{itemize}
    \item Health
        \begin{itemize}
            \item Detecting cancer on radon, Prof. Sauer/Forwiss research?
            \item Growing number of users are using smartphones sensors and related devices for 
                collating a range of health information, track regularly and detect patterns (noise?, privacy?)
        \end{itemize}
    \item Industry and Manufacturing
        \begin{itemize}
            \item quality assurance
        \end{itemize}
    \item Agriculture
        \begin{itemize}
            \item Detecting bad grains, $\rightarrow$ Hackzurich project
        \end{itemize}
\end{itemize}

\section{Limitations/Challenges}
Challenges

\section{Conclusion/Future Directions}
The conclusion goes here.

>>>>

\section{Algorithmic Foundations}
Before we take a closer look at the applications and challenges of CIL, first consider the 
following existing machine learning strategies and algorithms. As already mentioned above, 
there is a multitude of definitions for the term ML\@. But primarily, Arthur Samuel 
coined this term in 1959. Of course, a lot has changed in this area since then, 
however, the definition that ML allows computers to solve problems without being 
specifically programmed to do so, is still valid today\cite{MLStudiesUsingCheckers:samuel}.

Over the last decades, ML has developed significantly and has become an area of
research interest for many different actors, which makes it difficult to divide learning 
strategies into several categories. Different researchers are using different approaches 
for that\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
In the following section we want to present five strategies\cite{FoundationsOfML:mohri}.

@@

\subsection{Unsupervised learning}
In contrast to supervised learning, with this technique the learner only receives 
unlabeled training data and makes predictions for all unseen points. This technique is 
relatively similar to the way infants learn new things (e.g.\ learning a language) and 
is used, for example, in clustering data into groups\cite{BrainInf:holzinger}.

\subsection{Semi-supervised learning}
As the name suggests, the learner receives training data, which consists of both 
labeled as well as unlabelled data and makes predictions for all unseen points.
This technique is mainly used in areas where data is easily accessible, 
but finding the right label is expensive.

\subsection{Reinforcement Learning}\label{reinforcement}
Reinforcement learning is probably the oldest approach and a potentially important one for CIL\@. 
The learner interacts with his environment to gain new information. For each action 
he'll gets a reward. His goal is to maximize his reward over several repetitions. 
However, he is in conflict with using what has already been won by his actions 
or to get more information through further actions.

\subsection{Active Learning}\label{active}
The goal of Active Learning is to interact with other agents in a clever way in order 
to label already existing data points and thus achieve a similar performance at less available 
Information as in the method of supervised learning. To achieve this, 
the learner needs a selection strategy\cite{ActiveToDedicated:calma} that decides whether 
an action has enough information content to label a data point or not.

\section{When is using CIL helpful?}\label{AdvantageOfCIL}
In established ML systems, a separate model must be developed and trained in advance for 
each specific application. ML systems therefore have a relatively narrow application frame. 
The idea behind CIL systems is that they learn and self-organize knowledge throughout their lives. 
They collect information from various sources and evaluate the obtained data, so that they 
can solve problems together with other technical and human agents in a 
collaborative and interchangeable way\cite{CIL:sick}.
The CIL approach therefore deliberately integrates other intelligent systems 
(people and machines) into the decision-making process in order to ensure that the individual entities 
can solve otherwise difficult problems much easier.
Another difference to classical approaches is the mutual benefit. 
Machines not only benefit from training data of other agents, but also provide 
an own contribution to actively support people's collaboration processes by 
recognising their wishes and needs and reacting accordingly\cite{CIL:sick}.
\notes{D-CIL und O-CIL, obwohl man unterscheidet, betrachten wir hier nur allgemeines Modell.}

\section{Classification of CIL in Organic Computing}
CIL systems can be understood as organically structured information technology
which fulfill so-called self-x-properties\cite{Organic:schloer}\cite{Organic:schmeckt}.
They
\begin{itemize}
    \item configure themselves in the sense that they are not aligned by developers to an application case,
    \item optimize themselves by applying various strategies of ML to expand their knowledge,
    \item heal and protect themselves because cooperation with other systems is possible.
\end{itemize}
Depending on which methods of ML are used, CIL systems are also more or less self-explanatory 
during development\cite{Organic:schloer}.

\section{Application examples}
\subsection{Clustering}
Clustering is the perfect example of a starting point without sufficient information about a database. 
The basic goal here is to divide a data set into homogeneous groups of individual data points in order to create structure.
Clustering is used, for example, in most recommendation systems of popular Internet applications (Netflix movie recommendations, YouTube Video Tags \notes{[?]}) to group similar tags or find groups of people with a similar taste in movies.
Furthermore, clustering is used to identify communities in social networks, for example for target-advertising, or to cluster location-data so that "important places" of a person can be identified.

Unfortunately, real-world data in these areas is often unclean, contains false or unwanted data and is often present in 
dimensions $>$3, so that people alone, who are otherwise very good at recognizing similarities, are dependent on ML and vice-versa.

There are different approaches to cluster data into homogeneous groups. One of them is the k-Means algorithm\notes{[?]}. This requires at the beginning the number of $k$ clusters it should find. It then randomly places $k$ centroids in space, which should represent the center of a cluster, and assigns each item to the nearest centroid. After the assignment, each centroid is placed at the center of all items assigned to it. This process of assigning the items and moving the centroids to
the center is now repeated until the assignments of the items no longer change.

What all cluster algorithms have in common is that they need a way to compare data points for similarity.
Classically, data points are tried to display in an n-dimensional metric space and, for example, their Euclidean distance is measured for similarity.
The Euclidean distance between two data points $p = (p_1, p_2, \dots, p_n)$ and $q = (q_1, q_2, \dots, q_n)$ and thus their
similarity, when a small result means more similar, is defined as
\begin{equation}
    similarity(p, q) = \sqrt{\sum_{i=1}^{n} (q_i - p_i)^{2}}.
\end{equation}

Since data is usually multidimensional, i.e.\ much larger than three, suitable attributes must be selected for the comparison. 
However, the problem here is that similarity functions are influenced by subjective factors, since experts from different 
fields also find different partial aspects of the amount of data to be investigated interesting.
Therefore, the CIL approach can provide a decisive advantage in this case, as the knowledge and assessment of 
different experts and other systems can be used to make such decisions.
An interesting interactive approach follows\notes{[1]} to create a personal gazetteer from a users location data.

@@

\section{Challenges and future directions}
Challenges
Ethical Questions
